\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-09 doc/paper.tex
Participant info. Closes #155

	\section{User Study} \label{sec:userstudy} During development, we conducted a
	brief, four-participant user study to detect conflicts between our design and
	the goals in Section \ref{goals}. We designed the study to be exploratory;
	given trees based in the Enron dataset and at least twenty minutes, we asked
	the participants to adopt the persona of a consultant evaluating a company's
	spreadsheet practice, allowing for questions like which functions on which the
	employees most depended or which sheets or employees presented the most
	anomalous or dangerous designs. Though we instructed them on how to use the
	tool and suggested that they visit one of the most populous trees in the set,
	we put aside any specific tasks or questions and let them choose their own
	paths. Though interpretation of the phrase ``spreadsheet practice" can
	certainly vary from participant to participant, we readily accepted this
	interpretive flexibility since we wanted a range of views and backgrounds
	despite the persona. We clarified, furthermore, that their observations could
	be directed either at the quality of the data conveyed by the tool or at the
	tool's design itself. We present an overview of responses below, with the four
	participants recorded simply as P1 through P4. \par

>>>>

	\section{User Study} \label{sec:userstudy}

	We conducted a brief, exploratory user study during development to detect
	conflicts between our design and the goals in Section~\ref{goals}. In it, we
	gave the participants a set of visualizations from the Enron dataset and at
	least 20 minutes, and we asked them to adopt the persona of a consultant
	evaluating a company's spreadsheet practice. Through this framing, we intended
	to open the floor for questions like on which functions employees most depended
	and which sheets contained the most dangerous formula practice. We clarified,
	furthermore, that their observations could be directed either at the quality of
	the data conveyed by the tool or at the tool's design itself. \par

	We had four participants, labeled P1 through P4. Only P4 had no experience with
	spreadsheets in a professional environment, having used spreadsheets
	intermittently through university and hobbies. P1 through P3 all had varying
	levels of experience with spreadsheets in a professional capacity: P1 for 1
	year, P3 for 3, and P2 for 5. All participants were graduate students at the
	time of study but with some prior experience in industry, and we presented each
	with the same broad question about spreadsheet practice. Though interpretation
	of the phrase ``spreadsheet practice" can certainly vary from participant to
	participant, we readily accepted this interpretive flexibility since we wanted
	a range of views and backgrounds despite the persona.
